---
title: "Learning with Label Proportions"
author: "Huw Campbell"
date: "`r Sys.Date()`"
output: github_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE, message = FALSE}
library(nolabel)
library(dplyr)
library(Matrix)
library(pROC)
library(knitr)

print.data.frame <- function(x)
  kable(x[1:10, 1:7], row.names = F)

set.seed(123456)
```

Learning with Label Proportions (LLP) could be described
as the 4th learning framework, beside the more usual
supervised, unsupervised, and semi-supervised learning
ones.

In LLP, one does not have *any* fully labelled training
instances, they do however, have some statistical evidence,
in that instances grouped into certain bags have a proportion
of their instances being positive ones.

The dataset is provided in the form of (label, bag, features)
with the label being still the binary labels.
This is useful in case of testing the model.

```{r}
heart.sample <- heart[sample(nrow(heart)),]
test.fold    <- 1:(floor(nrow(heart.sample)/5))
testset      <- heart.sample[test.fold,]
trainset     <- heart.sample[-test.fold,]
proportions  <- (trainset %>% group_by(bag) %>%
  summarise( prop = length(label[label == 1]) / n()))$prop


print(trainset)
```

## Standard logistic regression with full labels

Firstly looking at standard logistic regression, i.e., we
have all the label information. The oracle function casts
logistic regression into the mean map framework, so one
could also use a `glm` here.

```{r}
w.lr      <- oracle(label ~ . -bag, trainset)
test.pred <- predict(w.lr, testset)
print(auc(testset$label, test.pred))
```

## Label proportion methods

Starting with a helper function:

```{r}
test_run <- function(...) {
  model     <- llp(bag ~ . -label, trainset, proportions, ...)
  test.pred <- predict(model, testset)
  print(auc(testset$label, test.pred))
}
```

```{r}
test_run(mode = "MM", alternating = F)
```

Laplacian Mean Map
```{r}
test_run(mode = "LMM", alternating = F)
```

Laplacian Mean Map with NC similarity
```{r}
test_run(mode = "LMM", similarity = "NC", alternating = F)
```

Alternating Mean Map with no mean map hints
```{r}
test_run()
```

Alternating Mean Map initialised with MM
```{r}
test_run(mode = "MM")
```

Alternating Mean Map initialised with LMM with NC similarity
```{r}
test_run(mode = "LMM", similarity = "NC")
```

Alternating Mean Map - Max, with no mean map hints
```{r}
test_run(max_order = T)
```
